IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-10 main.tex
:pencil: Rephrase discussion and add conclusion

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. The performance of the proposed design is compared with those of no IRS, non-adaptive (information-optimized, power-optimized) IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH). It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for single transmit antenna narrowband SWIPT.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
			% Though SWIPT has been subsequently investigated in many scenarios \cite{Clerckx2019}, it was noticed more recently that the modeling of the energy harvester, and in particular its nonlinearity, has a crucial and significant impact on the signal preference, resource allocation and system design of WPT and any wireless-powered systems \cite{Trotter2009,Clerckx2016a,Clerckx2019}.
			% , and recommended waveforms with large Peak-to-Average Power Ratio (PAPR) to improve the power efficiency and system coverage
			On the other hand, \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the rectifier input power level. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT. Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2019a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range. %Beyond WPT, the work in [10]
			The work was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery 2) a multicarrier unmodulated waveform superposed to a multicarrier modulated waveform is useful to enlarge the R-E region of SWIPT 3) a combination of power splitting and time sharing is in general the best strategy 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG) 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2017} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019b} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2017,Varasteh2019b} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2019a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2017} and new modulation schemes were subsequently designed.
		\end{subsection}

@@

			\textit{First}, we introduce an novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission to a single user. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2019b,Tang2019,Wu2019c,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

@@

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is demonstrated that the observations for SWIPT carries on to IRS-aided SWIPT. For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, and TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. In contrast to the active amplify-and-forward relay whose optimal location is around the midpoint \cite{Li2017}, we observed that the passive IRS should be placed next to either the transmitter or the receiver to further improve the R-E tradeoff, due to the product-distance path loss model. It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. Also, the adaptive IRS design outperformed the fixed (information-optimized, power-optimized) IRS for broadband transmission, and the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
			% single antenna, DoF -> new words. ff irs fs channel not all flexibility; active antenna -> frequency

@@

		The impact of the number of transmit antennas $M$ and IRS reflectors $L$ on the average R-E tradeoff is revealed in Fig.~\ref{fi:re_reflector} and \ref{fi:re_tx}. A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the number of components remains unchanged. Therefore, we conclude that the number of transmit antennas and reflectors have no impact on the waveform preference and transceiving strategy. A \textit{second} contrast suggests that active beamforming is more effective than passive beamforming, as the system performance is more sensitive to the variation of $M$ than $L$. Interestingly, the active MRT beamformer only has a transmit array gain of $M$. In comparison, the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$. However, the system performance in our setup is dominated by the direct link. As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}. Therefore, despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission and broadband transmission. The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary. In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve. To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total design flexibility of $NL$. Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in the presence of single transmit antenna would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
		\begin{equation}
			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/(h_{I,n,l}h_{R,n,l})\right)}}\,,\quad \forall n,l\,.
		\end{equation}
		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region in both cases. This is because IRS creates and adapts the weak extra channels such that they add constructively to enhance the composite channel. \textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission. The reason is that when $B=1\,\si{\MHz}$, all channels are approximately flat and the response of all subbands are roughly the same. In such cases, the additional design flexibility provided by the frequency selectivity of the ideal IRS would be unnecessary, because the the optimal reflection coefficients would almost align at all subbands. Similarly, WIT-optimized and WPT-optimized IRS boil down to optimizing a single term that represents the composite channel response at all subbands. As a consequence, all IRS strategies coincide with each other, and the optimal IRS for single transmit antenna narrowband SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands. On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments. Moreover, the WIT-optimized IRS tends to equalize the channel strength for all subbands as possible, due to the preference of WF strategy at high SNR. In comparison, the WPT-optimized IRS beams less towards few weakest subchannels, due to the inefficiency of small-amplitude tones in energy harvesting. Therefore, the adaptive IRS design is more suitable for broadband SWIPT. Note that the tradeoff for practical IRS indeed origins from frequency selectivity rather than number of subbands.
	\end{section}

>>>>

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. The performance of the proposed design is compared with those of no IRS, non-adaptive (information-optimized, power-optimized) IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH). It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission. The adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
			% Though SWIPT has been subsequently investigated in many scenarios \cite{Clerckx2019}, it was noticed more recently that the modeling of the energy harvester, and in particular its nonlinearity, has a crucial and significant impact on the signal preference, resource allocation and system design of WPT and any wireless-powered systems \cite{Trotter2009,Clerckx2016a,Clerckx2019}.
			% , and recommended waveforms with large Peak-to-Average Power Ratio (PAPR) to improve the power efficiency and system coverage
			On the other hand, \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the rectifier input power level. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT. Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2019a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range. %Beyond WPT, the work in [10]
			The work was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT 3) a combination of power splitting and time sharing is in general the best strategy 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG) 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2017} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019b} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2017,Varasteh2019b} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2019a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2017} and new modulation schemes were subsequently designed.
		\end{subsection}

@@

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2019b,Tang2019,Wu2019c,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

@@

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is demonstrated that the observations for SWIPT carries on to IRS-aided SWIPT. For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, and TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. In contrast to the active amplify-and-forward relay whose optimal location is around the midpoint \cite{Li2017}, we observed that the passive IRS should be placed next to either the transmitter or the receiver to further improve the R-E tradeoff, due to the product-distance path loss model. It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. Also, the adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.

			% single antenna, DoF -> new words. ff irs fs channel not all design flexibility; active antenna -> frequency

@@

		The impact of the number of transmit antennas $M$ and IRS reflectors $L$ on the average R-E tradeoff is revealed in Fig.~\ref{fi:re_reflector} and \ref{fi:re_tx}. A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the number remains unchanged. Therefore, we conclude that the number of transmit antennas and reflectors have no impact on the waveform preference and transceiving strategy. A \textit{second} contrast is that the system performance is more sensitive to the variation of $M$ than $L$. Interestingly, the active MRT beamformer only has a transmit array gain of $M$. In comparison, the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$. However, the system performance in our setup is dominated by the direct link. As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}. Therefore, despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance. Another explanation is that passive IRS has no design flexibility in the frequency domain (the reflection coefficients are the same for all subbands), while transmit antenna with RF-chains enables weight control over different subbands. Therefore, doubling the transmit antenna provides a bigger R-E region than doubling the IRS elements, and we conclude that active beamforming is more effective than passive beamforming.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission and broadband transmission. The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary. In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve. To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total design design flexibility of $NL$. Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in the presence of single transmit antenna would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
		\begin{equation}
			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/(h_{I,n,l}h_{R,n,l})\right)}}\,,\quad \forall n,l\,.
		\end{equation}
		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region in both cases. This is because IRS creates and adapts the weak extra channels that add constructively to enhance the composite channel. \textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission. The reason is that when $B=1\,\si{\MHz}$, the subchannel responses are very similar and the optimal passive beamforming would almost align at all subbands. That is to say, when the bandwidth is small, there is no enough frequency diversity for IRS to manipulate the subchannel strength such that all four IRS strategies coincide with each other. It implies that the passive beamforming only need to be optimized once for narrowband SWIPT, and a special case is that the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT. On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments. Moreover, the WIT-optimized IRS tends to equalize the channel strength for all subbands as possible, due to the preference of WF strategy at high SNR. In comparison, the WPT-optimized IRS beams less towards few weakest subchannels, due to the inefficiency of small-amplitude tones in energy harvesting. Therefore, adaptive IRS design is required for broadband SWIPT as information and energy receivers have different preference on the subchannel strength distribution.
	\end{section}

	\begin{section}{Conclusion and Future Works}
		This paper proposed a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the spectrum and energy efficiency of a single user. We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region. Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission with practical co-localized receiver architectures. Efficient algorithms based on GP, SCA, SDR and AO techniques are proposed to balance the system performance and computational complexity, which are numerically demonstrated to converge to a stationary point of the original problem for all tested channel realizations under different configurations. We confirmed that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff. When developed near the transmitter, IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range. Compared with active transmit antenna, it has no design flexibility in the frequency domain, but the passive characteristic significantly reduces the power consumption and enables noise-free reflection. Finally, adaptive passive beamforming is required for broadband transmission while the IRS only need to be optimized once for narrowband transmission.
		% For broadband SWIPT, adaptive passive beamforming for different R-E pairs is required, as ID and EH have different preference on the subchannel strength distribution. For narrowband SWIPT, the subchannel responses are very similar and the optimal passive beamforming for all R-E points coincide with each other. Therefore, the IRS only need to be optimized once.
		% that brings a quadratic array gain.

		The combination of IRS and SWIPT brings many possibilities and challenges. For example, how to optimize waveform, active and passive beamforming in a multiuser SWIPT system? How can multiple IRS cooperate with each other to benefit R-E tradeoff? How to perform channel estimation without RF-chains at the IRS? How to design IRS-aided SWIPT system under different multiple access techniques? How to implement IRS in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)? Can IRS operation be directly supported by SWIPT? Answers to these questions may bring a new wireless revolution.
	\end{section}
